% Created 2022-03-20 Sun 16:47
% Intended LaTeX compiler: pdflatex
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{unicode}
\usepackage{xcolor}
\definecolor{section}   {HTML}{80ADA3}
\definecolor{subsection}{HTML}{EAEAEA}
\definecolor{sidebar}   {HTML}{FAFAFA}
\pagenumbering{gobble}
\usepackage[margin=0.5in]{geometry}
\usepackage{paracol}
\usepackage[most]{tcolorbox}
\newtcolorbox{bgbox}[2][]{
width=\linewidth,
left=0pt, right=0pt, top=0pt, bottom=0pt,
colback=#2, colframe=#2,
arc=0pt,outer arc=0pt,
}
\newcommand{\sectionhead}[1]{%
\begin{bgbox}{section}%
{\Large \textsf{#1}}%
\end{bgbox}%
}
\newcommand{\subsectionhead}[1]{%
\begin{bgbox}{subsection}%
{\small \textsf{#1}}%
\end{bgbox}%
}
\usepackage[shortlabels]{enumitem}
\setlist{nosep}
\renewcommand{\labelitemii}{▻}
\renewcommand{\labelitemii}{▻}
\setlength{\parindent}{0em}
\usepackage{tabularx}
\date{}
\title{Matthew E. Adams Resume}
\hypersetup{colorlinks=false}
\begin{document}


\begin{center}
\sffamily
\begin{tabularx}{\textwidth}{Xr|l}
 & email & m2eadams@gmail.com\\
\raisebox{0pt}[0pt][0pt]{{\huge Matthew E. Adams } }  & phone & (650) 919-4152\\
Literature, Corpus Linguistics \& Digital Humanities & web & \href{https://phantisocracy.xyz}{\texttt{phantisocracy.xyz}}\\
 & github & \href{https://github.com/linguistgate}{\texttt{github.com/linguistgate}}\\
\end{tabularx}
\end{center}

\columnratio{0.65}
\begin{sloppypar} % The smaller linewidth causes issues otherwise.
\begin{paracol}{2}
\backgroundcolor{c[1]}{sidebar}
\switchcolumn % go to right column
\begin{raggedright}
\small

\sectionhead{Profile}
\label{Objectives}
\begin{itemize}
\item Currently based in the Salt Lake City area, I am looking to expand my career beyond education.
\item I am interested in data science, technical writing, and outdoors positions.
\item I have significant experience in quantitative computational work.
\end{itemize}
\sectionhead{Certifications}
\label{sec:org16fcf92}

\subsectionhead{California Clear Teaching Credential}
\label{sec:org6cfcadc}

\begin{itemize}
\item \textbf{Authorizations} English, History, and ELA
\item Document No. 180197982
\end{itemize}

\sectionhead{Skills}
\label{Skills}
\subsectionhead{Languages}
\label{Languages}
\begin{itemize}
\item \textbf{Fluent} German
\item \textbf{Advanced} French (reading)
\item \textbf{Beginner} French (speaking), Spanish, Korean
\end{itemize}

\subsectionhead{Programming}
\label{Programming}
\begin{itemize}
\item \textbf{Intermediate} Python
\item \textbf{Beginner} Lisp, Java, R
\end{itemize}

\subsectionhead{Other computer proficiencies}
\label{Other-computer-proficiencies}
\begin{itemize}
\item \textbf{Platforms} GNU/Linux, Mac, Windows
\item \textbf{Tools} Emacs, Org-mode, \LaTeX, Docker
\item \textbf{Version control} Git
\end{itemize}

\subsectionhead{Soft skills}
\label{Soft-skills}
\begin{itemize}
\item Teaching and mentoring
\item Literate programming
\item Proofreading and copy-editing
\end{itemize}

\subsectionhead{Teachables}
\label{Teachables}
\begin{itemize}
\item \textbf{Writing} Analytical prose, technical writing, creative writing
\item \textbf{Literature} British, American, German
\item \textbf{Linguistics} Formal phonology and syntax, corpus methods
\item \textbf{Knowledge management} Org-mode, notetaking, digital gardens
\end{itemize}

\end{raggedright}
\switchcolumn % go to left column


\sectionhead{Employment}
\label{Employment}
\small

\subsectionhead{English Faculty \& Writing Center Director \hfill Waterford School, 2019--Present}
\label{}
I teach English literature and run the Writing Center at Waterford School, a private liberal-arts institution in Sandy, Utah. I have developed a mentoring and coaching program between high school and middle school students and conducted more than 1,000 individual writing conferences.
\subsectionhead{Humanities Teacher \& Project Designer \hfill High Tech High, 2016--2019}
\label{}
I taught English and history in a project-based public charter school. I worked closely with local businesses to ensure that projects had real-life connections and with the math and science teacher to work on interdisciplinary coherence.
\subsectionhead{Computer Science Editor \hfill Shmoop, 2014--2015}
\label{computer-science-editor}
As computer science editor at this education start-up, I hired and managed a small team of writers developing courses in computer programming and edited their writing for clarity, correctness, and humor.
\subsectionhead{Postdoctoral Scholar \hfill University of Düsseldorf, 2013--2014}
\label{sec:orge7ac019}
Following work on my dissertation, I began research on the relationship between word frequency and morphological behavior.
\subsectionhead{German Legal Proofreader \hfill Geotext, 2011--2014}
\label{Geotext}
I proofed German-to-English legal documents. One of my biggest caseloads was the Madoff set of legal actions, and I worked closely with German and Austrian translators.
\subsectionhead{Research \& Teaching Assistant \hfill Stanford University, 2007--2012}
\label{research-teaching-asst}
I assisted in the instruction of eight courses, some of them graduate-level, and worked on three research projects with Professors Arto Anttila, Dan Jurafsky, and Joan Bresnan. I served as the Mentor Teaching Assistant, developing a course on pegagogy, and was the Graduate Student Representative for 2007--2008.
\subsectionhead{German Instructor \hfill Georgetown University, 2003--2005}
\label{german-instructor}
I taught intermediate German courses and was actively involved in curriculum reform efforts, drawing on statistical methods and CHILDES data to inform improvements.
\sectionhead{Education}
\label{Education}
\subsectionhead{Ph.D. in Linguistics \hfill Stanford University, 2014}
\label{}
Thesis: \emph{The Comparative Grammaticality of the English Comparative}
\subsectionhead{M.A. in German \hfill Georgetown University, 2005}
\label{M.Sc. in-Computer-Science}
Highest Distinction on Oral Examination of Master's thesis
\subsectionhead{Affiliate Scholar in German \hfill Georg-August Universität Göttingen, 2000--2001}
\label{Affilate-Scholar}

\subsectionhead{B.A. in Linguistics and German \hfill University of California, Irvine, 2002}
\label{B.A.-German-Linguistics}
\begin{itemize}
\item \emph{Summa cum Laude} in Linguistics
\item \emph{Magna cum Laude} in German
\end{itemize}

\end{paracol}
\end{sloppypar}
\newpage
\sectionhead{Awards \& Recognition}
\label{Awards}
\subsectionhead{Professional and academic}
\label{sec:org0a2b1ed}

\begin{center}
\begin{tabular}{ll}
\hline
\textbf{Name} & \textbf{Year}\\
\hline
UCSD San Diego Area Writing Project Fellowship (\emph{declined}) & 2017\\
Fulbright Scholarship to Berlin, Germany (\emph{declined}) & 2003\\
UC Irvine School of Social Sciences Order of Merit (Top 2\%) & 2002\\
Phi Beta Kappa & 2000\\
AATG \emph{Pädagogischer Austauschdienst} Study Program & 1997\\
\hline
\end{tabular}
\end{center}

\subsectionhead{Graduate studies scholarships and fellowships}
\label{Graduate-studies-scholarships-and-fellowships}
\begin{center}
\begin{tabular}{llr}
\hline
\textbf{Name} & \textbf{Years held} & \textbf{Value}\\
\hline
Deutscher Akademischer Austauschdienst Fellowship & 2014--2015 & \$17,500\\
Stanford Europe Center Grant & 2014--2015 & \$5,000\\
Linguistic Society of America Institute Fellowship & 2009 & \$6,000\\
Stanford Linguistics Department Funding & 2008--2012 & \$60,000\\
Bud Milligan Fellowship & 2006--2008 & \$24,000\\
Georgetown University Full Funding & 2003--2005 & \$30,000\\
\hline
\end{tabular}
\end{center}
\sectionhead{Publications}
\label{Publications}
\small

\begin{itemize}
\item \href{https://scholar.google.com/citations?user=-k9s2XwAAAAJ\&hl=en}{Matthew Adams}. (2017). Prosodic well-formedness and comparative grammaticality: morphology and periphrasis in the English comparative. In Vera Gribanova and Stephanie Shih, editors, \emph{The morphosyntax-phonology connection: locality and directionality at the interface} (pp. 197--222), Oxford University Press, Oxford.
\item \href{https://scholar.google.com/citations?user=-k9s2XwAAAAJ\&hl=en}{Matthew Adams}, \emph{\href{https://searchworks.stanford.edu/view/10530947}{The Comparative Grammaticality of the English Comparative}}, Doctoral dissertation, Stanford University, 2014.
\item Arto Anttila, Matthew Adams, and Mike Speriosu. (2010). \href{http://www.tandfonline.com/doi/full/10.1080/01690960903525481}{The role of prosody in the English dative alternation}. \emph{Language and Cognitive Processes}, 25, 946--981.
\end{itemize}

\sectionhead{Personal}
\label{Extracurricular}
\begin{itemize}
\item Portfolio at \href{https://phantisocracy.xyz}{\texttt{phantisocracy.xyz}}
\item Avid backpacker of California, Utah, and Europe
\end{itemize}

\vfill
This document available in multiple formats from
\url{https://github.com/linguistgate/resume/}.
\end{document}